\documentclass[a3paper,14pt]{extarticle}

\usepackage[utf8x]{inputenc}
\usepackage{enumerate}

\usepackage{setspace}
\setlength{\parindent}{0.0cm}

\usepackage[margin=2.54cm]{geometry}
\pagenumbering{gobble}

\renewcommand*{\familydefault}{\sfdefault}

\begin{document}
\section*{\centerline{Code of Conduct}\label{code-of-conduct}}

\emph{This Code of Conduct applies to all CSSA-run spaces, including the
Common Room, Facebook group, Facebook page, and during CSSA events.}\\[4pt]

Everyone in the Common Room and interacting in other spaces that the
CSSA moderates (the Facebook group, the Facebook page, and during CSSA
events) is required to agree with the following code of conduct. CSSA
Committee Members and Common Room Officers will enforce this code. We
expect cooperation from everyone to help ensure a safe environment for
everybody.\\[1pt]

\textbf{tl;dr: Be excellent with each other}

\subsection*{Need Help?}\label{need-help}

Talk to one of the committee members or common room officers. Their
names and photos are on the poster on the left.

\subsection*{The Quick Version}\label{the-quick-version}

The CSSA is dedicated to keeping our spaces harassment-free
for everyone, regardless of gender, gender identity, gender expression,
age, sexual orientation, disability, physical appearance, body size,
race, or religion (or lack thereof). We do not tolerate harassment of
people in this space in any form. Please respect the common room as a
shared space for all our members. Members violating these rules may be
sanctioned or expelled from the common room at the discretion of the
CSSA Committee or Common Room Officers.

\subsection*{The Less Quick Version}\label{the-less-quick-version}

Harassment includes offensive verbal comments related to gender, gender
expression, age, sexual orientation, disability, physical appearance,
body size, race, religion, as well as sexual and or excessively violent 
images in public spaces, deliberate intimidation, stalking, following, 
harassing photography or recording, sustained disruption, inappropriate 
physical contact, and unwelcome sexual attention.\\[1pt]

Members asked to stop any harassing behaviour are expected to comply
immediately.\\[1pt]
 
If people engage in harassing behaviour, committee members or common
room officers may take any action they deem appropriate, including
warning the offender or expulsion from the common room.\\[1pt]

If you are being harassed, notice that someone else is being harassed,
or have any other concerns, please contact a member of the CSSA
Committee or a Common Room Officer immediately. These people and ways to
contact them can be identified from the poster to the left (``CSSA
Committee and Common Room Officers'').

\subsection*{A few other things}\label{a-few-other-things}

\begin{itemize}
\item
  Alcohol is not to be stored or consumed in the common room.
\item
  This is a shared space -- keep the volume to a reasonable level, and
  use headphones if you are playing loud music, videos, or playing
  games. Loud can be taken as `above quiet conversation'.
\item
  Keep the common room clean -- pick up rubbish (bins are next to the
  fridge, and also in the corridor), even if it is not yours.
\item
  If a discussion or argument escalates to a point where it is
  distressing other members, the parties responsible may be asked to
  leave.
\end{itemize}

\subsection*{Feedback and Reporting}\label{feedback-and-reporting}

If you have feedback for the CSSA Committee about the Common Room,
\textbf{including reports of inappropriate behaviour}, please send an
email to the \textbf{President}, the \textbf{Vice-President}, and the
\textbf{Common-Room Representative}, using the emails on the poster to
the left. If a report involves one of those people, just include the
other two.\\[12pt]

\emph{Version 3.3}
\end{document}
